Concentration of Maxima and Fundamental Limits in High-Dimensional Testing and Inference

### 2021-04-04 3.phase_transitions/3.global-tests.tex
many changes... Chapter 4 intro WIP

The optimality of sparse signal detection was first studied by \citet{ingster1998minimax}, who showed that a phase transition in the $r$-$\beta$ plane exists for the signal detection problem. 
Specifically, consider the so-called {\em detection boundary} function:
\begin{equation} \label{eq:detection-boundary-large-signals}
    f(\beta) = 
    \begin{cases}
        \max\{0,\beta -1/2\} & 0<\beta\le 3/4\\
        \left(1 - \sqrt{1-\beta}\right)^2 & 3/4 < \beta \le 1.
    \end{cases}
    \quad\quad \beta\in (0,1].
\end{equation} 
Assume that the non-zero signal sizes are all equal and parameterized as $\sqrt{2{r}\log{p}}$.
If the signal size parameter $r$ is {\em above} the detection boundary, i.e., $r>f(\beta)$, then the global null 
hypothesis $\mu(i)=0$ for all $i=1,\dots,p$ can be distinguished from the alternative as $p\to\infty$ in the sense of \eqref{eq:support-recovery-success} using the likelihood ratio test.  Otherwise, when the signal sizes fall below the boundary, i.e., $r< f(\beta)$, no test can do better than a 
random guess.  We visualize the detection boundary in the upper panel of Figure
\ref{fig:phase-diagram-signal-detection}.

Adaptive tests such as Tukey's \ac{HC} in \eqref{eq:HC-statistic} \citep{donoho2004higher} and a modified 
goodness-of-fit test statistic of \citet{zhang2002powerful} have been identified to attain this performance limit 
without knowledge of the sparsity and signal sizes. It is also known that the max-statistic \eqref{eq:max-statistic} is only efficient when $r>(1+\sqrt{1-\beta})^2$, and is therefore sub-optimal for denser signals where $1/2\le\beta\le 3/4$; see \cite{cai2011optimal}.
In contrast, the sum-of-square-type statistics such as $L_2$ was shown in \cite{fan1996test} to be asymptotically powerless when the $L_2$-norm of the signal $\|\mu\|_2^2$ is $o(\sqrt{p})$, or equivalently, when $\beta>1/2$ in our parametrization.

Notice that the scaling for the signal magnitude $\Delta = \sqrt{2r\log{p}}$ is useful for studying very sparse signals ($\beta>1/2$), but fails to reveal the difficulties of the detection problems when the signals are relatively dense 
($\beta<1/2$).  This is because $f(\beta) = 0,\ \beta\in (0,1/2]$. Thus, a different scaling is needed to study the regime of
small but dense signals.  In this case, with slight overloading of notation, we parametrize signal sizes as 
\begin{equation} \label{eq:signal-size-small} 
    \underline{\Delta} = p^{\underline{r}}
    \le \mu(i) \le
    \overline{\Delta} = p^{\overline{r}}, \quad \text{for all}\;\;i\in S_p,
\end{equation}
where $\underline{r}$ and $\overline{r}$ are {\rm negative} constants and 
the signal magnitude vanishes, as $p\to\infty$.
In this scaling, for the so-called faint signal regime, \citet{cai2011optimal} established a phase 
transition result characterized by the following boundary,
\begin{equation} \label{eq:detection-boundary-small-signals}
    f_s(\beta) = \beta - 1/2, \quad 0 < \beta \le 1/2.
\end{equation} 
Specifically, if $\overline{r}<f_s(\beta)$, the signal detection fails in the sense of \eqref{eq:support-recovery-failure} regardless of the procedures, while the \ac{HC} statistic continues to attain asymptotically perfect detection when $\underline{r}>f_s(\beta)$. 
We visualize this boundary in the lower panel of Figure \ref{fig:phase-diagram-signal-detection}.

\begin{figure}
      \centering
      \includegraphics[width=0.7\textwidth]{figures/phase_diagram_signal_detection.eps}
      \includegraphics[width=0.7\textwidth]{figures/phase_diagram_signal_detection_vanishing_signals.eps}
      \caption{The phase diagrams of the sparse signal detection problem. 
      Signal size and sparsity are parametrized by $r$ and $\beta$, respectively.
      % Signal sparsity $|S|$ is parametrized by $\beta$. 
      % Signal sizes $\Delta$, parametrized by $r$, increases with dimension $p$ inside the upper panel, and decreases with $p$ inside the power panel.
      The diagrams illustrate the regions where the signal detection problem can be solved asymptotically by some of the commonly used statistics: the maximum ($M$), the sum-of-squares ($L_2$), the sum-of-absolute values ($L_1$), and the sum ($T$).
      In each region of the diagram, the annotated statistics can make the detection risk \eqref{eq:risk-detection} vanish, as dimension $p$ diverges. Conversely, the risks has liminf at least one.
      The detection problem is unsolvable for very sparse and weak signals in the undetectable regions.
      Notice that the $L_1$ and $L_2$ statistics are in fact sub-optimal for all sparsity levels.
      On the other hand, the max-statistic remains powerful for sparse signals ($\beta>1/2$), and is fully efficient when the problem is very sparse ($\beta\ge3/4$).
      The \ac{HC} statistic can detect signals in all configurations in the detectable regions.
      See text and Theorem \ref{thm:detection-optimality}.}
      \label{fig:phase-diagram-signal-detection}
\end{figure}

>>>>

The optimality of sparse signal detection was first studied by \citet{ingster1998minimax}, who showed that a phase transition in the $r$-$\beta$ plane exists for the signal detection problem. 
Specifically, consider the so-called {\em detection boundary} function:
\begin{equation} \label{eq:detection-boundary-large-signals}
    f_{\mathrm{D}}(\beta) = 
    \begin{cases}
        \max\{0,\beta -1/2\} & 0<\beta\le 3/4\\
        \left(1 - \sqrt{1-\beta}\right)^2 & 3/4 < \beta \le 1.
    \end{cases}
    \quad\quad \beta\in (0,1].
\end{equation} 
Assume that the non-zero signal sizes are all equal and parameterized as $\sqrt{2{r}\log{p}}$.
If the signal size parameter $r$ is {\em above} the detection boundary, i.e., $r>f_{\mathrm{D}}(\beta)$, then the global null 
hypothesis $\mu(i)=0$ for all $i=1,\dots,p$ can be distinguished from the alternative as $p\to\infty$ in the sense of \eqref{eq:support-recovery-success} using the likelihood ratio test.  Otherwise, when the signal sizes fall below the boundary, i.e., $r< f_{\mathrm{D}}(\beta)$, no test can do better than a 
random guess.  We visualize the detection boundary in the upper panel of Figure
\ref{fig:phase-diagram-signal-detection}.

Adaptive tests such as Tukey's \ac{HC} in \eqref{eq:HC-statistic} \citep{donoho2004higher} and a modified 
goodness-of-fit test statistic of \citet{zhang2002powerful} have been identified to attain this performance limit 
without knowledge of the sparsity and signal sizes. 
It is also known that the max-statistic \eqref{eq:max-statistic} is only efficient when $r>(1+\sqrt{1-\beta})^2$, and is therefore sub-optimal for denser signals where $1/2\le\beta\le 3/4$; see \cite{cai2011optimal}. 
(Recently, \cite{li2020optimality} showed that in the more general setting where signals themselves are dispersed, the sub-optimality of the max statistic disappears in the detection problem.)
In contrast, the sum-of-square-type statistics such as $L_2$ was shown in \cite{fan1996test} to be asymptotically powerless when the $L_2$-norm of the signal $\|\mu\|_2^2$ is $o(\sqrt{p})$, or equivalently, when $\beta>1/2$ in our parametrization.

Notice that the scaling for the signal magnitude $\Delta = \sqrt{2r\log{p}}$ is useful for studying very sparse signals ($\beta>1/2$), but fails to reveal the difficulties of the detection problems when the signals are relatively dense 
($\beta<1/2$).  This is because $f_{\mathrm{D}}(\beta) = 0,\ \beta\in (0,1/2]$. Thus, a different scaling is needed to study the regime of
small but dense signals.  In this case, with slight overloading of notation, we parametrize signal sizes as 
\begin{equation} \label{eq:signal-size-small} 
    \underline{\Delta} = p^{\underline{r}}
    \le \mu(i) \le
    \overline{\Delta} = p^{\overline{r}}, \quad \text{for all}\;\;i\in S_p,
\end{equation}
where $\underline{r}$ and $\overline{r}$ are {\rm negative} constants and 
the signal magnitude vanishes, as $p\to\infty$.
In this scaling, for the so-called faint signal regime, \citet{cai2011optimal} established a phase 
transition result characterized by the following boundary,
\begin{equation} \label{eq:detection-boundary-small-signals}
    f_{\mathrm{D}'}(\beta) = \beta - 1/2, \quad 0 < \beta \le 1/2.
\end{equation} 
Specifically, if $\overline{r}<f_{\mathrm{D}'}(\beta)$, the signal detection fails in the sense of \eqref{eq:support-recovery-failure} regardless of the procedures, while the \ac{HC} statistic continues to attain asymptotically perfect detection when $\underline{r}>f_{\mathrm{D}'}(\beta)$. 
We visualize this boundary in the lower panel of Figure \ref{fig:phase-diagram-signal-detection}.

\begin{figure}
      \centering
      \includegraphics[width=0.7\textwidth]{figures/phase_diagram_signal_detection.eps}
      \includegraphics[width=0.7\textwidth]{figures/phase_diagram_signal_detection_vanishing_signals.eps}
      \caption{The phase diagrams of the sparse signal detection problem. 
      Signal size and sparsity are parametrized by $r$ and $\beta$, respectively.
      % Signal sparsity $|S|$ is parametrized by $\beta$. 
      % Signal sizes $\Delta$, parametrized by $r$, increases with dimension $p$ inside the upper panel, and decreases with $p$ inside the power panel.
      The diagrams illustrate the regions where the signal detection problem can be solved asymptotically by some of the commonly used statistics: the maximum ($M$), the sum-of-squares ($L_2$), the sum-of-absolute values ($L_1$), and the sum ($T$).
      In each region of the diagram, the annotated statistics can make the detection risk \eqref{eq:risk-detection} vanish, as dimension $p$ diverges. Conversely, the risks has liminf at least one.
      The detection problem is unsolvable for very sparse and weak signals in the undetectable regions.
      Notice that the $L_1$ and $L_2$ statistics are in fact sub-optimal for all sparsity levels.
      On the other hand, the max-statistic remains powerful for sparse signals ($\beta>1/2$), and is fully efficient when the problem is very sparse ($\beta\ge3/4$).
      The \ac{HC} statistic can detect signals in all configurations in the detectable regions; we explicitly marked the region where signals are only detectable by \ac{HC} among the statistics considered.
      See the text and Theorem \ref{thm:detection-optimality}.}
      \label{fig:phase-diagram-signal-detection}
\end{figure}

### 2021-04-04 4.exact_support_recovery/4.phase_transition_results.tex
many changes... Chapter 4 intro WIP

\begin{theorem} \label{thm:sufficient}
Let the errors have common marginal distribution $F\in \text{AGG}(\nu)$ with $\nu>0$.
Let $\widehat{S}_p$ be the Bonferroni's procedure \eqref{eq:Bonferroni-procedure} with vanishing FWER $\alpha = \alpha(p) \to 0$, such that %\fbox{slower than any polynomial}
$\alpha p^\delta\to \infty$ for every $\delta>0$.
If
\begin{equation} \label{eq:signal-above-boundary}
    \underline{r} > g(\beta) = (1 + (1 - \beta)^{1/\nu})^\nu,
\end{equation}
then we have
\begin{equation} \label{eq:exact-supporot-recovery}
    \lim_{p\to\infty}\sup_{\mu\in\Theta_p^+(\beta, \underline{r})} \P[\widehat{S}_p \neq S_p] = 0.
\end{equation}
\end{theorem}
\begin{proof}%[Proof of Theorem \ref{thm:sufficient}]
Throughout the proof, the dependence on $p$ will be suppressed to simplify notations when such omissions do not lead to ambiguity.

@@

\begin{example} \label{exmp:FWER-controlling_procedures}
Under Gaussian errors, the particular choice of the thresholding at $t_p = \sqrt{2\log{p}}$ in \eqref{eq:Bonferroni-procedure} corresponds to a Bonferroni's procedure with FWER decreasing at a rate of ${\cal O}((\log{p})^{-1/2})$, and hence Theorem \ref{thm:sufficient} applies. 
By Corollary \ref{cor:FWER-controlling_procedures}, Holm's procedure --- and when the errors are independent, the {\v{S}}id{\'a}k, and Hochberg procedures --- with FWER controlled at $(\log{p})^{-1/2}$ all achieve perfect support recovery provided that $\underline{r}>g(\beta)$.

@@

\begin{remark} \label{rmk:sufficient-strengthened}
In the proof of Theorem \ref{thm:sufficient}, both \eqref{eq:Bonferroni-FWER-control} and \eqref{eq:sufficient-proof-eq2} hold uniformly over all error dependence structures.
Therefore, \eqref{eq:exact-supporot-recovery-FWER} and \eqref{eq:exact-supporot-recovery-FWNR} may be strengthened to yield
\begin{equation} \label{eq:exact-supporot-recovery-strengthened}
    \lim_{p\to\infty}\sup_{\substack{\mu\in\Theta_p^+(\beta, \underline{r})\\ {\cal E}\in D(F)}} P[\widehat{S}_p \neq S_p] = 0,
\end{equation}
for $\underline{r} > g(\beta)$, where $D(F)$ is the collection of all arrays with common marginal $F$, i.e., 
\begin{equation} \label{eq:common-marginal-distribution}
    D(F)=\{{\cal E}=(\epsilon_p(i))_p:\;\epsilon_p(i)\sim F\;\text{for all }i=1,\ldots,p, \text{and}\; p=1,2,\ldots\}.
\end{equation}
\end{remark}

@@

\begin{theorem} \label{thm:necessary}
    Let ${\cal E}$ be a triangular array with common $\text{AGG}(\nu)$ marginal $F$, $\nu > 0$.
    % Let the signal $\mu$ have $|S_p| = \lfloor p^{(1-\beta)} \rfloor$ non-zero entries where $\beta\in(0,1]$, where the signal sizes $\mu(i)$, $i\in S_p$ are at most $\overline{\Delta} = \left(\nu\overline{r}\log p\right)^{1/\nu}$.
    % and the signals $\mu$ have $s=|S|=\lfloor p^{1-\beta}\rfloor$ be as described in Theorem \ref{thm:sufficient}. 
    Assume further that the errors ${\cal E}$ have uniform relatively stable maxima and minima, i.e., ${\cal E}\in U(F)$, and $(-{\cal E}) = \{-\epsilon_{p}(i)\} \in U(F)$.
    If 
    \begin{equation} \label{eq:signal-below-boundary}
        \overline{r} < g(\beta) = \left(1+(1-\beta)^{1/\nu}\right)^\nu,
    \end{equation}
    then
    \begin{equation} \label{eq:classification-impossible-dependent}
        \lim_{p\to\infty} \inf_{\widehat{S}_p\in{\cal T}} \inf_{\mu\in{\Theta_p^-(\beta, \overline{r})}} \P[\widehat{S}_p \neq S_p] = 1,
    \end{equation}
    where ${\cal T}$ is the class of all thresholding procedures \eqref{eq:thresholding-procedure}.
\end{theorem}
\begin{proof} %[Proof of Theorem \ref{thm:necessary}]
To avoid cumbersome double subscript notations, we will sometimes suppress dependence on $p$ of the set sequences $\widehat{S}_p$ and $S_p$ in the proof.

@@

\begin{remark}[Minding the gap] \label{rmk:gap-between-sufficient-necessary}
The sufficient condition in Theorem \ref{thm:sufficient} requires that \emph{all} signals be larger than the strong classification boundary $g(\beta)$ in order to achieve exact support recovery \eqref{eq:exact-recovery}, while Theorem \ref{thm:necessary} states that exact support recovery fails (in the sense of \eqref{eq:exact-recovery-failure}) when \emph{all} signal sizes are below the boundary --- the two conditions are \emph{not} complements of each other.
This gap between the sufficient and necessary conditions on signal sizes, however, may be difficult to bridge.
Indeed, in general, when signal sizes straddle the boundary $g(\beta)$, either outcome is possible, as we demonstrate in 
Example \ref{exmp:signals-straddling-the-boundary} below.
\end{remark}

@@

Consider two scenarios
\begin{enumerate}
    \item $r^{(1)} = (1+\delta)g(\beta)$, $r^{(2)} = (1+\delta)$ with $|S_p^{(1)}|=|S_p|-1$, $|S_p^{(2)}|=1$, 
    \item $r^{(1)} = (1+\delta)g(\beta)$, $r^{(2)} = (1-\delta)g(\beta)$ with $|S_p^{(1)}|=\lfloor|S_p|/2\rfloor$, $|S_p^{(2)}|=|S_p| - |S_p^{(1)}|$.
\end{enumerate}
for some constants $0<\delta<1-\beta<1$. 
In both cases, signals in $S_p^{(1)}$ (respectively, $S_p^{(2)}$) are above (respectively, below) the strong classification boundary \eqref{eq:strong-classification-boundary}.
However, in the first scenario, we have $\mathbb{P}[\widehat{S}^{\text{Bonf}}_p=S_p]\to 1$ where $\widehat{S}^{\text{Bonf}}_p$ is the Bonferroni's procedure described in Theorem \ref{thm:sufficient}, 
while in the second scenario, we have $\mathbb{P}[\widehat{S}_p=S_p]\to 0$ for \emph{all} thresholding procedures $\widehat{S}_p$.

@@

In the second scenario, the signal sizes in $S^{(2)}$ by definition fall below the strong classification boundary \eqref{eq:strong-classification-boundary}.
To see that no thresholding procedure succeeds, we adapt the proof of Theorem \ref{thm:necessary}.
In particular, we obtain
$$
    \P[\widehat{S}_p = S_p] 
    \le \P\left[\max_{j\in S^c}x(j) \le t_p < \min_{j\in S}x(j)\right]
    \le \P\left[\max_{j\in S^c}x(j) < \min_{j\in S^{(2)}}x(j)\right].
$$
By the assumption that signals in $S^{(2)}$ have size parameter $(1-\delta)g(\beta)$, we have
\begin{equation}
\P\left[\max_{j\in S^c}x(j) < \min_{j\in S^{(2)}}x(j)\right]
= \P\left[ \frac{M_{S^{c}}}{u_p} < \frac{\sqrt{2(1-\delta)g(\beta)\log{p}} - m_{S^{(2)}}}{u_p}\right], 
\end{equation}
where $M_{S^{c}} = \max_{j\in S^{c}}\epsilon(j)$ and $m_{S^{(2)}} = \max_{j\in S^{(2)}}\left(-\epsilon(j)\right)$.
The ratio on the left-hand-side of the inequality converges to 1 as in \eqref{eq:classification-possible-dependent-proof-3} in the main text, whereas the term on the right-hand-side
\begin{align*}
    \frac{\sqrt{2(1-\delta)g(\beta)\log{p}} - m_{S^{(2)}}}{u_p} 
    &= \sqrt{(1-\delta)g(\beta)} - \frac{m_{S^{(2)}}}{u_{|S^{(2)}|}} \frac{u_{|S^{(2)}|}}{u_p} \\
    &\xrightarrow{\P} \sqrt{(1-\delta)} + \sqrt{1-\beta}(\sqrt{(1-\delta)} - 1) < 1.
\end{align*}
where we used the URS of the error arrays, and that 
$$
u_{|S^{(2)}|} \sim \sqrt{2\log{(p^{1-\beta}/2)}} 
= \sqrt{2(({1-\beta})\log{p}-\log2)} \sim \sqrt{2({1-\beta})\log{p}}.
$$
to conclude the convergence in probability.
\end{proof}
\end{example}

Our second comment is on the interplay between thresholding procedures and the dependence class characterized by URS.
\begin{remark} \label{rmk:dependence-assumptions}
Paraphrasing Theorems \ref{thm:sufficient} and \ref{thm:necessary}: 
if we consider only thresholding procedures, then for a very large class of dependence structures, we cannot improve upon the Bonferroni procedure $\widehat{S}_p^{\text{Bonf}}$. 
Specifically, for all ${\cal E}\in U(F)$ and ${-\cal E}\in U(F)$, and for all $S_p\in {\cal S}$, where $\mathcal{S} = \left\{S\subseteq\{1,\ldots,p\};|S|=\lfloor p^{1-\beta}\rfloor\right\}$, we have
\begin{equation}
    \lim_{p\to\infty} \P[\widehat{S}_p^{\text{Bonf}}\neq S_p]
    = \begin{cases}
    \limsup_{p\to\infty} \inf_{\widehat{S}_p \in {\cal T}} \P[\widehat{S}_p\neq S_p] = 0, & \text{if}\quad \underline{r} > g(\beta),\\
    \liminf_{p\to\infty} \inf_{\widehat{S}_p \in {\cal T}} \P[\widehat{S}_p\neq S_p] = 1, & \text{if}\quad \overline{r} < g(\beta)\\
    \end{cases}
\end{equation}
where $\cal T$ is the set of all thresholding procedures \eqref{eq:thresholding-procedure}.

Theorem \ref{thm:necessary} answers a question raised in \citet{butucea2018variable}.
In particular, the authors of \citep{butucea2018variable} commented that independent error is the  `least favorable model' in the problem of support recovery, and 
conjectured that the support recovery problem may be easier to solve under dependence, similar to how the problem of signal detection is easier under dependent 
errors \citep{hall2010innovated}. 
Surprisingly, our results here state that asymptotically, \emph{all} error dependence structures in the large URS class are equally difficult for \emph{thresholding procedures}. Therefore, the phase transition behavior is universal in the class of dependence structures characterized by URS.
For more details, see also Section \ref{sec:minimax}.
\end{remark}

\begin{remark} We emphasize that the restriction to the URS dependence class in Theorem \ref{thm:necessary} is 
\emph{not} an assumption of convenience. 
The dependence condition characterized by uniform relative stability is, in fact, the weakest of its kind in the literature.
We will characterize the class URS dependence class in Chapter \ref{chap:URS} below.
\end{remark}

@@

\begin{remark}
Notice that the boundary for the signal size parameter is identically $1$ in this dense regime.
Therefore, if we interpret $\beta = 0$ of the parametrization \eqref{eq:sparsity-parametrized} as $s\sim cp$, where $c\in(0,1)$, then the strong classification boundary \eqref{eq:strong-classification-boundary} may be continuously extended to the left-end point where $g(0)=1$.
\end{remark}

>>>>

\begin{theorem} \label{thm:sufficient}
Let the errors have common marginal distribution $F\in \text{AGG}(\nu)$ with $\nu>0$.
Let $\widehat{S}_p$ be the Bonferroni's procedure \eqref{eq:Bonferroni-procedure} with vanishing FWER $\alpha = \alpha(p) \to 0$, such that %\fbox{slower than any polynomial}
$\alpha p^\delta\to \infty$ for every $\delta>0$.
If
\begin{equation} \label{eq:signal-above-boundary}
    \underline{r} > f_{\mathrm{E}}(\beta) = (1 + (1 - \beta)^{1/\nu})^\nu,
\end{equation}
then we have
\begin{equation} \label{eq:exact-supporot-recovery}
    \lim_{p\to\infty}\sup_{\mu\in\Theta_p^+(\beta, \underline{r})} \P[\widehat{S}_p \neq S_p] = 0.
\end{equation}
\end{theorem}
\begin{proof}%[Proof of Theorem \ref{thm:sufficient}]
Throughout the proof, the dependence on $p$ will be suppressed to simplify notations when such omissions do not lead to ambiguity.

@@

\begin{example} \label{exmp:FWER-controlling_procedures}
Under Gaussian errors, the particular choice of the thresholding at $t_p = \sqrt{2\log{p}}$ in \eqref{eq:Bonferroni-procedure} corresponds to a Bonferroni's procedure with FWER decreasing at a rate of ${\cal O}((\log{p})^{-1/2})$, and hence Theorem \ref{thm:sufficient} applies. 
By Corollary \ref{cor:FWER-controlling_procedures}, Holm's procedure --- and when the errors are independent, the {\v{S}}id{\'a}k, and Hochberg procedures --- with FWER controlled at $(\log{p})^{-1/2}$ all achieve perfect support recovery provided that $\underline{r}>f_{\mathrm{E}}(\beta)$.

@@

\begin{remark} \label{rmk:sufficient-strengthened}
In the proof of Theorem \ref{thm:sufficient}, both \eqref{eq:Bonferroni-FWER-control} and \eqref{eq:sufficient-proof-eq2} hold uniformly over all error dependence structures.
Therefore, \eqref{eq:exact-supporot-recovery-FWER} and \eqref{eq:exact-supporot-recovery-FWNR} may be strengthened to yield
\begin{equation} \label{eq:exact-supporot-recovery-strengthened}
    \lim_{p\to\infty}\sup_{\substack{\mu\in\Theta_p^+(\beta, \underline{r})\\ {\cal E}\in D(F)}} P[\widehat{S}_p \neq S_p] = 0,
\end{equation}
for $\underline{r} > f_{\mathrm{E}}(\beta)$, where $D(F)$ is the collection of all arrays with common marginal $F$, i.e., 
\begin{equation} \label{eq:common-marginal-distribution}
    D(F)=\{{\cal E}=(\epsilon_p(i))_p:\;\epsilon_p(i)\sim F\;\text{for all }i=1,\ldots,p, \text{and}\; p=1,2,\ldots\}.
\end{equation}
\end{remark}

@@

\begin{theorem} \label{thm:necessary}
    Let ${\cal E}$ be a triangular array with common $\text{AGG}(\nu)$ marginal $F$, $\nu > 0$.
    % Let the signal $\mu$ have $|S_p| = \lfloor p^{(1-\beta)} \rfloor$ non-zero entries where $\beta\in(0,1]$, where the signal sizes $\mu(i)$, $i\in S_p$ are at most $\overline{\Delta} = \left(\nu\overline{r}\log p\right)^{1/\nu}$.
    % and the signals $\mu$ have $s=|S|=\lfloor p^{1-\beta}\rfloor$ be as described in Theorem \ref{thm:sufficient}. 
    Assume further that the errors ${\cal E}$ have uniform relatively stable maxima and minima, i.e., ${\cal E}\in U(F)$, and $(-{\cal E}) = \{-\epsilon_{p}(i)\} \in U(F)$.
    If 
    \begin{equation} \label{eq:signal-below-boundary}
        \overline{r} < f_{\mathrm{E}}(\beta) = \left(1+(1-\beta)^{1/\nu}\right)^\nu,
    \end{equation}
    then
    \begin{equation} \label{eq:classification-impossible-dependent}
        \lim_{p\to\infty} \inf_{\widehat{S}_p\in{\cal T}} \inf_{\mu\in{\Theta_p^-(\beta, \overline{r})}} \P[\widehat{S}_p \neq S_p] = 1,
    \end{equation}
    where ${\cal T}$ is the class of all thresholding procedures \eqref{eq:thresholding-procedure}.
\end{theorem}
\begin{proof} %[Proof of Theorem \ref{thm:necessary}]
To avoid cumbersome double subscript notations, we will sometimes suppress dependence on $p$ of the set sequences $\widehat{S}_p$ and $S_p$ in the proof.

@@

\begin{remark}[Minding the gap] \label{rmk:gap-between-sufficient-necessary}
The sufficient condition in Theorem \ref{thm:sufficient} requires that \emph{all} signals be larger than the strong classification boundary $f_{\mathrm{E}}(\beta)$ in order to achieve exact support recovery \eqref{eq:exact-recovery}, while Theorem \ref{thm:necessary} states that exact support recovery fails (in the sense of \eqref{eq:exact-recovery-failure}) when \emph{all} signal sizes are below the boundary --- the two conditions are \emph{not} complements of each other.
This gap between the sufficient and necessary conditions on signal sizes, however, may be difficult to bridge.
Indeed, in general, when signal sizes straddle the boundary $f_{\mathrm{E}}(\beta)$, either outcome is possible, as we demonstrate in 
Example \ref{exmp:signals-straddling-the-boundary} below.
\end{remark}

@@

Consider two scenarios
\begin{enumerate}
    \item $r^{(1)} = (1+\delta)f_{\mathrm{E}}(\beta)$, $r^{(2)} = (1+\delta)$ with $|S_p^{(1)}|=|S_p|-1$, $|S_p^{(2)}|=1$, 
    \item $r^{(1)} = (1+\delta)f_{\mathrm{E}}(\beta)$, $r^{(2)} = (1-\delta)f_{\mathrm{E}}(\beta)$ with $|S_p^{(1)}|=\lfloor|S_p|/2\rfloor$, $|S_p^{(2)}|=|S_p| - |S_p^{(1)}|$.
\end{enumerate}
for some constants $0<\delta<1-\beta<1$. 
In both cases, signals in $S_p^{(1)}$ (respectively, $S_p^{(2)}$) are above (respectively, below) the strong classification boundary \eqref{eq:strong-classification-boundary}.
However, in the first scenario, we have $\mathbb{P}[\widehat{S}^{\text{Bonf}}_p=S_p]\to 1$ where $\widehat{S}^{\text{Bonf}}_p$ is the Bonferroni's procedure described in Theorem \ref{thm:sufficient}, 
while in the second scenario, we have $\mathbb{P}[\widehat{S}_p=S_p]\to 0$ for \emph{all} thresholding procedures $\widehat{S}_p$.

@@

In the second scenario, the signal sizes in $S^{(2)}$ by definition fall below the strong classification boundary \eqref{eq:strong-classification-boundary}.
To see that no thresholding procedure succeeds, we adapt the proof of Theorem \ref{thm:necessary}.
In particular, we obtain
$$
    \P[\widehat{S}_p = S_p] 
    \le \P\left[\max_{j\in S^c}x(j) \le t_p < \min_{j\in S}x(j)\right]
    \le \P\left[\max_{j\in S^c}x(j) < \min_{j\in S^{(2)}}x(j)\right].
$$
By the assumption that signals in $S^{(2)}$ have size parameter $(1-\delta)f_{\mathrm{E}}(\beta)$, we have
\begin{equation}
\P\left[\max_{j\in S^c}x(j) < \min_{j\in S^{(2)}}x(j)\right]
= \P\left[ \frac{M_{S^{c}}}{u_p} < \frac{\sqrt{2(1-\delta)f_{\mathrm{E}}(\beta)\log{p}} - m_{S^{(2)}}}{u_p}\right], 
\end{equation}
where $M_{S^{c}} = \max_{j\in S^{c}}\epsilon(j)$ and $m_{S^{(2)}} = \max_{j\in S^{(2)}}\left(-\epsilon(j)\right)$.
The ratio on the left-hand-side of the inequality converges to 1 as in \eqref{eq:classification-possible-dependent-proof-3} in the main text, whereas the term on the right-hand-side
\begin{align*}
    \frac{\sqrt{2(1-\delta)f_{\mathrm{E}}(\beta)\log{p}} - m_{S^{(2)}}}{u_p} 
    &= \sqrt{(1-\delta)f_{\mathrm{E}}(\beta)} - \frac{m_{S^{(2)}}}{u_{|S^{(2)}|}} \frac{u_{|S^{(2)}|}}{u_p} \\
    &\xrightarrow{\P} \sqrt{(1-\delta)} + \sqrt{1-\beta}(\sqrt{(1-\delta)} - 1) < 1.
\end{align*}
where we used the URS of the error arrays, and that 
$$
u_{|S^{(2)}|} \sim \sqrt{2\log{(p^{1-\beta}/2)}} 
= \sqrt{2(({1-\beta})\log{p}-\log2)} \sim \sqrt{2({1-\beta})\log{p}}.
$$
to conclude the convergence in probability.
\end{proof}
\end{example}

Our second remark is on the restriction to thresholding procedures.
\begin{remark}
	we emphasize that the sharp phase transition result just established apply only to the general class of thresholding procedures. It is natural to ask if we have left out the other good procedures in this restriction.
	We will establish in Chapter \ref{chap:optimality} below that in many cases the optimal procedures are in fact thresholding procedures. In general, however, thresholding procedures can be sub-optimal, e.g., when the errors have heavy (regularly-varying) tails. 
	We will also demonstrate the absence of a phase transition phenomenon in exact support recovery by thresholding, in Supplement Section \ref{suppsec:heavy-tailed}. 
\end{remark}

Our final comment is on the interplay between thresholding procedures and the dependence class characterized by URS.
\begin{remark} \label{rmk:dependence-assumptions}
Paraphrasing Theorems \ref{thm:sufficient} and \ref{thm:necessary}: if we consider only thresholding procedures, then for a very large class of dependence structures, we cannot improve upon the Bonferroni procedure $\widehat{S}_p^{\text{Bonf}}$. 
Specifically, for all ${\cal E}\in U(F)$ and ${-\cal E}\in U(F)$, and for all $S_p\in {\cal S}$, where $\mathcal{S} = \left\{S\subseteq\{1,\ldots,p\};|S|=\lfloor p^{1-\beta}\rfloor\right\}$, we have
\begin{equation}
    \lim_{p\to\infty} \P[\widehat{S}_p^{\text{Bonf}}\neq S_p]
    = \begin{cases}
    \limsup_{p\to\infty} \inf_{\widehat{S}_p \in {\cal T}} \P[\widehat{S}_p\neq S_p] = 0, & \text{if}\quad \underline{r} > f_{\mathrm{E}}(\beta),\\
    \liminf_{p\to\infty} \inf_{\widehat{S}_p \in {\cal T}} \P[\widehat{S}_p\neq S_p] = 1, & \text{if}\quad \overline{r} < f_{\mathrm{E}}(\beta)\\
    \end{cases}
\end{equation}
where $\cal T$ is the set of all thresholding procedures \eqref{eq:thresholding-procedure}.

Theorem \ref{thm:necessary} answers a question raised in \citet{butucea2018variable}.
In particular, the authors of \citep{butucea2018variable} commented that independent error is the  `least favorable model' in the problem of support recovery, and 
conjectured that the support recovery problem may be easier to solve under dependence, similar to how the problem of signal detection is easier under dependent 
errors \citep{hall2010innovated}. 
Surprisingly, our results here state that asymptotically, \emph{all} error dependence structures in the large URS class are equally difficult for \emph{thresholding procedures}. Therefore, the phase transition behavior is universal in the class of dependence structures characterized by URS.
%For more details, see also Section \ref{sec:minimax}.
\end{remark}

The restriction to the URS dependence class in Theorem \ref{thm:necessary} is \emph{not} an assumption of convenience. 
The dependence condition characterized by uniform relative stability is, in fact, one of the weakest in the literature.
We will characterize the class URS dependence class in Chapter \ref{chap:URS} below.

@@

\begin{remark}
Notice that the boundary for the signal size parameter is identically $1$ in this dense regime.
Therefore, if we interpret $\beta = 0$ of the parametrization \eqref{eq:sparsity-parametrized} as $s\sim cp$, where $c\in(0,1)$, then the strong classification boundary \eqref{eq:strong-classification-boundary} may be continuously extended to the left-end point where $f_{\mathrm{E}}(0)=1$.
\end{remark}
